---
title: "Internal Assessment Questions (10 February 2021)"
author: "pravesh"
date: "2020-09-18"
output: html_document
---

**Instructions:**

1. *You have eight questions of 5 marks each. You need to attempt all. *
1. *Download the files and save them on your desktop.* 
1. *Open a new excel workbook and save it in your roll number, e.g. ECON01. For backlog candidates you can save it as BL-ECON01 *
1. *For example if you are solving question 1 then copy the data and paste/save it to sheet 1 of ECON01 workbook. Similarly, for Q2 copy-paste the data in sheet 2 of the workbook ECON01. Rename the worksheets 1 & 2 as Q1 and Q2 respectively. Do this for the rest. *
1. *At the end save your workbook and email (pravesh.econ@presiuniv.ac.in) it to me. Note that you will have just one workbook to send to.*

Answer the following: [$8\times5 = 40$]

1. In the [Decadeincome.xlsx](Decadeincome.xlsx) file, you are given a sample of incomes (in thousands of 1980 dollars) for a set of families sampled in 1980 and 1990. Assume that these families are representative of the whole United States. Republicans claim that the country was better off in 1990 than in 1980 because average income increased. Do you agree?
1. In 1970 and 1971, eligibility for the US armed services draft was determined on the basis of a draft lottery number. The number was determined by birth date. A total of 366 balls, one for each possible birth date, were placed in a container and shaken. The first ball selected was given the number 1 in the lottery, the second ball the number 2, and so on. Men whose birthdays corresponded to the lowest numbers were drafted first. The [Draftlottery.xlsx](Draftlottery.xlsx) file contains the actual results of the 1970 and 1971 drawings. For example, in the 1970 drawing, January 1 received the number 305. Use descriptive statistics to demonstrate that the 1970 draft lottery was not random and the 1971 lottery was random. (Hint: Use the AVERAGE and MEDIAN functions to compute the mean and median lottery number for each month.)
1. The [Coltsdata.xlsx](Coltsdata.xlsx) file contains yards gained by the 2006 Indianapolis Colts on each rushing and passing play. Describe how the outcomes of rushing plays and passing plays differ.
1. The Problem 3 worksheet of [Ch56data.xlsx](Ch56data.xlsx) contains annual returns on stocks, T-bills, and T-bonds. Find and interpret the correlations between the annual returns on these three classes of investments.
1. In the Problem 3 worksheet of [Ch56data.xlsx](Ch56data.xlsx) find and interpret the partial correlations considering each variable constant each time. (For e.g. if you are considering the partial correlation between stocks and T-bills given T-bonds, your next task would be finding partial correlation between stocks and T-bonds given T-bills, and so on).
1. Suppose that the firm's production function is $Q = F(K,L)= 50K^{0.5}L^{0.5}$. Suppose, too, that the price of labour $w=5$ and the price of capital $r=20$. What is the cost minimising input bundle if the firm wants to produce $1,000$ units per year? (David Besanko, Ronald R. Braeutigam. Microeconomics. Wiley.) 
1. Jason makes diamond bracelets, necklaces, and earrings. He wants to work a maximum of 160 hours per month. He has 800 ounces of diamonds. The profit, labor time, and ounces of diamonds required to produce each product are as follows. If demand for each product is unlimited, how can Jason maximize his profit?
     ```{r, echo=FALSE, warning=FALSE, message=FALSE}
     library(tidyverse)
     tibble(
     Product = c("Bracelet", "Necklace", "Earrings"),
     `Unit profit` = c("$300", "$200", "$100"),
     `Labor hours per unit` = c(0.35,0.15, 0.05),
     `Ounces of diamonds per unit` = c(1.2, 0.75, 0.5)
     ) %>% 
     knitr::kable(align = "c")
     ```
     In your product mix example, suppose that whenever you sell more than 400 pounds of any product, you must give a $\$1$ per pound discount on each pound above 400 sold. How does this change the answer to the problem?
1. A computer manufacturing plant produces mice, keyboards, and video game joysticks. The per-unit profit, per-unit labor usage, monthly demand, and per-unit machine-time usage are given in the following table:
     ```{r,echo=FALSE, warning=FALSE, message=FALSE}
  library(tidyverse)
  tibble(
  ` `  = c("Profit/unit", "Labour usage/unit", "Machine time/unit","Monthly demand"),
  Mice = c("$8", "0.2 hour", "0.4 hour", "15000"),
  Keyboards = c("$11", "0.3 hour", "0.055 hour", "29,000"),
  Joystics = c("$9", "0.24 hour", "0.04 hour", "11,000")
  ) %>%
    knitr::kable(align = c("l","c", "c", "c"), position = "center")
     ```
     Each month, a total of 13,000 labor hours and 3,000 hours of machine time are available. How can the manufacturer maximize its monthly profit contribution from the plant?
